When are Fuzzy Extractors Possible?

### 2014-09-24 info-bounds/FuzzyExtPossibility.tex
stuck on isoperimetric proof

\subsubsection{Computational secure sketches}
Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. is uses HILL entropy.

@@

\begin{corollary}
\label{cor:rec yields sketch}
Let $\mathcal{Z}$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+t\delta)$. 
\end{corollary}

\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).  Unpredictable secure sketches is implied by virtual-grey box obfuscation of point functions~\cite{BitanskyCKP14}.

@@

Consider some $p^*\in A_{ss}$.  We now show that $H_0(V | p^*) \le XXXX$\bnote{fill in}.  Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p$ is at least $(1-2\epsilon)2^\kappa$.  Note that, $R|P=p$ is the set of possible keys.

@@

Note that $\bnd(Q_{p^*, r}) \cap \inter(Q_{p,r}) =\emptyset$, for any $r_1, r_2$, $\inter(Q_{p^*, r_1}) \cap \inter(Q_{p^*, r_2}) =\emptyset$ and the union of all boundaries and interiors is the entire space.  Furthermore, note that for any $r\in \zo^\kappa$,  $\Pr[V\in Q_{p^*, r}] = \ngl(n).$\bnote{need to fill in this distinguishing argument, note this doesn't need to be the case for all $p^*$ just on average. need another markov inequality.}\bnote{what can we say about the relative sizes of these spaces?}

>>>>

\subsubsection{Extending to Computational secure sketches}
Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. is uses HILL entropy.

@@

%\begin{corollary}
%\label{cor:rec yields sketch}
%Let $\mathcal{Z}$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $\mathcal{Z}^n$, with $\rec'$ of circuit size $s_{rec}$.
%If $s_{sec}\geq t(s_{rec} + n\log |\mathcal{Z}|)$, then there exists a   $(\mathcal{Z}^n, n\log |\mathcal{Z}|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
%$4(\epsilon+t\delta)$. 
%\end{corollary}

\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).  Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.

@@

Consider some $p^*\in A_{ss}$.  We now show that $H_0(V | p^*) \le XXXX$\bnote{fill in}.  Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  Note that, $R|P=p$ is the set of possible keys.

@@

Note that $\bnd(Q_{p^*, r}) \cap \inter(Q_{p,r}) =\emptyset$.  We now show $Q$ are small.

\begin{claim} For any $r\in \zo^\kappa$,  $ | Q_{p^*, r}| \le (1+\epsilon)2^\kappa.$
\end{claim}
\begin{proof} 
Recall that for any $r$, $\Pr[U = r] = 1/2^\kappa$.  Since the total statistical distance is $2\epsilon$, 
\[
\Pr[R=r] \le 2( 2\epsilon + \Pr[U=r]) = 4\epsilon + 2^{-\kappa+1}.
\] 
The distribution $R | P=p^*  \overset{def}= \rep(V | P=p^*, p^*)$.  Thus, the overall probability $\Pr[V|P=p^* \in Q_{r, P^*}] \le 4\epsilon+2^{-\kappa +1}$.  \bnote{how to continue from here?  this doesn't talk about the size of $V|P=p^*$.}
\end{proof}
